A Study of Experiment Repeatability

### 2017-03-10 pt_characterization/repeatability_test/paper.tex
Chracterizing draft

\begin{document}
\title{Histogram on Recent Runs by EMPv5}

@@

\section{Description}
This document presents histograms based on the most recent runs 
of a program under test, called {\em INC}, over its increasing task lengths.

@@

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period\\ \hline
{\tt sodb9} &  INC1$\sim$INC1024 & Each run with 300 samples & 2017-02-09 $\sim$ 2017-02-10 / 2017-02-12 $\sim$ 2017-02-19\\ \hline
{\tt sodb10} & INC2048 & A run of 300 samples & 2017-02-12 $\sim$ 2017-02-20\\ \hline
{\tt sodb12} & INC4096 & A run of 300 samples & 2017-02-12 $\sim$ 2017-02-27\\ \hline
{\tt sodb12} & INC8192 & Two runs, each with 40 samples & 2017-01-16 $\sim$ 2017-01-20 / 2017-01-25 $\sim$ 2017-01-29\\ \hline
{\tt sodb12} & INC16384 & Two runs, each with 40 samples & 2017-01-05 $\sim$ 2017-01-13 / 2017-01-29 $\sim$ 2017-02-06\\ \hline 
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes}}
\end{table}

>>>>

\begin{document}
\title{A Study of Experiment Repeatability}

@@

\section{Description}
This document presents histograms rendered based on empirical data 
of a program under test, called {\em INC}. 
Our experiment increases a task length of {\em INC} 
from one second to 4096 seconds by a factor of two.
We already ran this experiment last month (February 2017), 
but we reran the experiment this month (March 2017) 
to check if experiment repeatability holds true.

@@

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|p{4cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period\\ \hline
{\tt sodb9} &  INC1$\sim$INC512 & Each run with 1000 samples & 2017-03-02 $\sim$ 2017-03-07\\ \hline
%{\tt sodb10} & INC2048 & A run of 300 samples & 2017-02-12 $\sim$ 2017-02-20\\ \hline
%{\tt sodb12} & INC4096 & A run of 300 samples & 2017-02-12 $\sim$ 2017-02-27\\ \hline
%{\tt sodb12} & INC8192 & Two runs, each with 40 samples & 2017-01-16 $\sim$ 2017-01-20 / 2017-01-25 $\sim$ 2017-01-29\\ \hline
%{\tt sodb12} & INC16384 & Two runs, each with 40 samples & 2017-01-05 $\sim$ 2017-01-13 / 2017-01-29 $\sim$ 2017-02-06\\ \hline 
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes}}
\end{table}

### 2017-03-10 pt_characterization/repeatability_test/sodb9/res.tex
Chracterizing draft

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_et_hist_v5.eps}
		\label{fig:inc128_et_hist_v5}
	}
	\subfigure[ET frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_et_hist_v5.eps}
		\label{fig:inc256_et_hist_v5}
	}
	\subfigure[ET frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_et_hist_v5.eps}
		\label{fig:inc512_et_hist_v5}
	}
	\subfigure[ET frequency on INC1024]{
		\includegraphics[scale=0.43]{sodb9/1024_sec_et_hist_v5.eps}
		\label{fig:inc1024_et_hist_v5}
	}
	\caption{ET Histograms of INC128 ... INC1024~\label{fig:s9_et_hist3}}
\end{figure}

\pagebreak

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC2048]{
		\includegraphics[scale=0.43]{sodb10/2048_sec_et_hist_v5.eps}
		\label{fig:inc2048_et_hist_v5}
	}
	\subfigure[ET frequency on INC4096]{
		\includegraphics[scale=0.43]{sodb12/4096_sec_et_hist_v5.eps}
		\label{fig:inc4096_et_hist_v5}
	}
	\subfigure[ET frequency on INC8192]{
		\includegraphics[scale=0.43]{sodb12/8192_sec_et_hist2_v5.eps}
		\label{fig:inc8192_et_hist_v5}
	}
	\subfigure[ET frequency on INC16384]{
		\includegraphics[scale=0.43]{sodb12/16384_sec_et_hist2_v5.eps}
		\label{fig:inc16384_et_hist_v5}
	}
	\caption{ET Histograms of INC2048 ... INC16384~\label{fig:s9_et_hist4}}
\end{figure}

\pagebreak

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC8192]{
		\includegraphics[scale=0.43]{sodb12/8192_sec_et_hist_v5.eps}
		\label{fig:inc8192_et_hist_all_v5}
	}
	\subfigure[ET frequency on INC16384]{
		\includegraphics[scale=0.43]{sodb12/16384_sec_et_hist_v5.eps}
		\label{fig:inc16384_et_hist_all_v5}
	}
	\caption{ET Histograms of INC8192... INC16384 [combined with 2015's run]~\label{fig:s9_et_hist5}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\subfigure[PT frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_pt_hist_v5.eps}
		\label{fig:inc256_hist_v5}
	}
	\subfigure[PT frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_pt_hist_v5.eps}
		\label{fig:inc512_hist_v5}
	}
	\subfigure[PT frequency on INC1024]{
		\includegraphics[scale=0.43]{sodb9/1024_sec_pt_hist_v5.eps}
		\label{fig:inc1024_hist_v5}
	}
	\caption{PT Histograms of INC256 ... INC1024~\label{fig:s9_pt_hist3}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC2048]{
		\includegraphics[scale=0.43]{sodb10/2048_sec_pt_hist_v5.eps}
		\label{fig:inc2048_hist_v5}
	}
	\subfigure[PT frequency on INC4096]{
		\includegraphics[scale=0.43]{sodb12/4096_sec_pt_hist_v5.eps}
		\label{fig:inc4096_hist_v5}
	}
	\subfigure[PT frequency on INC8192]{
		\includegraphics[scale=0.43]{sodb12/8192_sec_pt_hist2_v5.eps}
		\label{fig:inc8192_hist_v5}
	}
	\subfigure[PT frequency on INC16384]{
		\includegraphics[scale=0.43]{sodb12/16384_sec_pt_hist2_v5.eps}
		\label{fig:inc16384_hist_v5}
	}
	\caption{PT Histograms of INC2048 and INC16384~\label{fig:s9_pt_hist4}}
\end{figure}

\pagebreak

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC8192]{
		\includegraphics[scale=0.43]{sodb12/8192_sec_pt_hist_v5.eps}
		\label{fig:inc8192_hist_all_v5}
	}
	\subfigure[PT frequency on INC16384]{
		\includegraphics[scale=0.43]{sodb12/16384_sec_pt_hist_v5.eps}
		\label{fig:inc16384_hist_all_v5}
	}
	\caption{PT Histograms of INC8192 and INC16384 [combined with 2015's run]~\label{fig:s9_pt_hist5}}
\end{figure}

>>>>

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_et_hist_v5.eps}
		\label{fig:inc128_et_hist_v5}
	}
	\subfigure[ET frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_et_hist_v5.eps}
		\label{fig:inc256_et_hist_v5}
	}
	\subfigure[ET frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_et_hist_v5.eps}
		\label{fig:inc512_et_hist_v5}
	}
%	\subfigure[ET frequency on INC1024]{
%		\includegraphics[scale=0.43]{sodb9/1024_sec_et_hist_v5.eps}
%		\label{fig:inc1024_et_hist_v5}
%	}
	\caption{ET Histograms of INC128 ... INC512~\label{fig:s9_et_hist3}}
\end{figure}

%\pagebreak
%
%\begin{figure}[hp!]
%	\centering
%	\subfigure[ET frequency on INC2048]{
%		\includegraphics[scale=0.43]{sodb10/2048_sec_et_hist_v5.eps}
%		\label{fig:inc2048_et_hist_v5}
%	}
%	\subfigure[ET frequency on INC4096]{
%		\includegraphics[scale=0.43]{sodb12/4096_sec_et_hist_v5.eps}
%		\label{fig:inc4096_et_hist_v5}
%	}
%	\subfigure[ET frequency on INC8192]{
%		\includegraphics[scale=0.43]{sodb12/8192_sec_et_hist2_v5.eps}
%		\label{fig:inc8192_et_hist_v5}
%	}
%	\subfigure[ET frequency on INC16384]{
%		\includegraphics[scale=0.43]{sodb12/16384_sec_et_hist2_v5.eps}
%		\label{fig:inc16384_et_hist_v5}
%	}
%	\caption{ET Histograms of INC2048 ... INC16384~\label{fig:s9_et_hist4}}
%\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\subfigure[PT frequency on INC256]{
		\includegraphics[scale=0.43]{sodb9/256_sec_pt_hist_v5.eps}
		\label{fig:inc256_hist_v5}
	}
	\subfigure[PT frequency on INC512]{
		\includegraphics[scale=0.43]{sodb9/512_sec_pt_hist_v5.eps}
		\label{fig:inc512_hist_v5}
	}
%	\subfigure[PT frequency on INC1024]{
%		\includegraphics[scale=0.43]{sodb9/1024_sec_pt_hist_v5.eps}
%		\label{fig:inc1024_hist_v5}
%	}
	\caption{PT Histograms of INC256 ... INC512~\label{fig:s9_pt_hist3}}
\end{figure}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[PT frequency on INC2048]{
%		\includegraphics[scale=0.43]{sodb10/2048_sec_pt_hist_v5.eps}
%		\label{fig:inc2048_hist_v5}
%	}
%	\subfigure[PT frequency on INC4096]{
%		\includegraphics[scale=0.43]{sodb12/4096_sec_pt_hist_v5.eps}
%		\label{fig:inc4096_hist_v5}
%	}
%	\subfigure[PT frequency on INC8192]{
%		\includegraphics[scale=0.43]{sodb12/8192_sec_pt_hist2_v5.eps}
%		\label{fig:inc8192_hist_v5}
%	}
%	\subfigure[PT frequency on INC16384]{
%		\includegraphics[scale=0.43]{sodb12/16384_sec_pt_hist2_v5.eps}
%		\label{fig:inc16384_hist_v5}
%	}
%	\caption{PT Histograms of INC2048 and INC16384~\label{fig:s9_pt_hist4}}
%\end{figure}
